Resonant Scattering in a Uniform Sphere with Large Optical Depth

### 2020-12-10 ms.tex
adding two-stream approx comparison with Dijkstra et al 2006, still need to write out equations

@@

@@

For each numerical solution, the monochromatic source of photons was initialized with a different starting frequency to evaluate the analytic solutions' accuracy with variation of the parameter $\rm \sigma_s$. This is related to $\rm x_{init}$ by

\begin{equation} \label{sigma0_xinit}
    \sigma_0 = \frac{\beta}{a} \rm x_{init}^3
\end{equation}

Monte Carlo numerical simulations were performed with $\rm x_{init} = (0.0, 2.0, 4.0 ... 12.0)$ and optical depths $\tau_0 = (10^6, 10^7)$. In Fig. \ref{fig:sol_mc_residual_0}, \ref{fig:sol_mc_residual_6} and \ref{fig:sol_mc_residual_12}, these are compared with the analytic solutions at selected initial frequencies. In each of these figures, the contribution of the flux from Eq. \ref{eq:Hbc} is examined alongside the solutions $H_{\rm d}$ and $H_{\rm 0}$. The corrected solution, $H_{\rm 0 + bc} = H_{\rm 0} + H_{\rm bc}$, has considerably lower residuals to Monte Carlo than the other solutions, especially in the line wing. It is evident that the solution $H_{\rm d}$ derived by \citet{1973MNRAS.162...43H} diverges significantly from the Monte Carlo simulations in the line wings. The $H_{\rm bc}$ correction term, when added to the solution $H_0$ derived by \citet{2006ApJ...649...14D}, produces a successful analytical result that characterizes the probability distribution of frequencies for escaping photons, including situations in which the photons are given initial frequencies outside of the line core.

>>>>

The main impediment to peforming magnetohydrodynamic simulations with fully a coupled radiative transfer solution via Monte Carlo methods is the prohibitive computational cost. A primary factor in the cost of Monte Carlo is that the number of scatterings a photon (packet/superphoton?) undergoes is proportional to the line center optical depth.  Near the base of the atmosphere individual simulation cells can have optical depths of more than a million so most of the time is spent integrating photons in these cells. This means that any method that can treat these zone via an analytic solution has the potential to greatly accelerate the calculation.

There are several methods that are commonly used to accelerate Monte Carlo radiation transfer calculations.  The simplest class of methods that is specific to resonance line transfer are core skipping methods \citep{1968ApJ...153..783A,2002ApJ...567..922A}.  These methods focus Monte Carlo transfer on the wings of the line and avoid scatterings in the core. Line core photons are pushed to the wings by biasing the atomic velocity distribution to high velocities so tha opacity is lower and escape is more rapid.

A second class of methods are hydbrid diffusion methods \citep{2001JCoPh.172..543G}, such as discrete diffusion Monte Carlo \citep{2007JCoPh.222..485D}. This involves designating sufficiently optically thick simulations cells for computation via a finite difference representaiton of radiation transfer equation. This method is particularly attractive for gray opacity applications where a single diffusion equation can be computed.  For the resonant scattering problem, where the opacity is a strong function of frequnecy, implementation of this method is more complex and computationally demanding as it requires the solution of many frequency groups, but can lead to a considerable speed up \citep{2018MNRAS.479.2065S}.

A third class of methods are modified random walk methods \citep{1984JCoPh..54..508F,2009A&A...497..155M,Robitaille2010}. In this case a spherical volume (usually the largest within a simulation cell) is chosen when the scattering mean-free-path is small compared with the zone size.  An outgoing photon is then randomly sampled on the surface of this outgoing sphere by drawing its properties from distributions in outgoing frequencies, directions and escape times, based on solutions to the diffusion equation withing a uniform sphere.

@@

% TODO: (Connor) Fill out the rest of this paragraph and include equations
Rewriting Eq. C17 from \citet{2006ApJ...649...14D} in our notation, a comparison can be made with the surface flux derived from their closed-form solution, Eq. \ref{eq:H0surf}. Under the two-stream approximation, it is expected that the boundary condition in Eq. \ref{eq:bc} hold true if the solutions are consistent.

@@

For each numerical solution, the monochromatic source of photons was initialized with a different starting frequency to evaluate the analytic solutions' accuracy with variation of the parameter $\rm \sigma_s$. This is related to $\rm x_{init}$ by 
\begin{equation} \label{sigma0_xinit}
    \sigma_0 = \frac{\beta}{a} \rm x_{init}^3
\end{equation}

where $\beta = \sqrt{2 \pi ^2 / 27}$. Monte Carlo numerical simulations were performed with $\rm x_{init} = (0.0, 2.0, 4.0 ... 12.0)$ and optical depths $\tau_0 = (10^6, 10^7)$. In Fig. \ref{fig:sol_mc_residual_0}, \ref{fig:sol_mc_residual_6} and \ref{fig:sol_mc_residual_12}, these are compared with the analytic solutions at selected initial frequencies. In each of these figures, the contribution of the flux from Eq. \ref{eq:Hbc} is examined alongside the solutions $H_{\rm d}$ and $H_{\rm 0}$. The corrected solution, $H_{\rm 0 + bc} = H_{\rm 0} + H_{\rm bc}$, has considerably lower residuals to Monte Carlo than the other solutions, especially in the line wing. It is evident that the solution $H_{\rm d}$ derived by \citet{1973MNRAS.162...43H} diverges significantly from the Monte Carlo simulations in the line wings. The $H_{\rm bc}$ correction term, when added to the solution $H_0$ derived by \citet{2006ApJ...649...14D}, produces a successful analytical result that characterizes the probability distribution of frequencies for escaping photons, including situations in which the photons are given initial frequencies outside of the line core.
